%Bryan Tidwell latex resume
\documentclass[11pt,oneside]{article}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage[T1]{fontenc}
\pdfinfo{
/Title (Resume)
/Author (Bryan Tidwell)
/Subject (Resume)
/Keywords (FullStack, BackEnd, Java, SpringBoot, SQL, git, vagrant, Struts, Android, Intellij, JSP, HTML, C, Bash, Devops, IoT, javascript, elixir, python, vim   )
}

\pagestyle{empty}
\geometry{letterpaper,tmargin=0.25in,bmargin=0in,lmargin=.75in,rmargin=1in,headheight=0in,headsep=0in,footskip=.2in}

\setlength{\parindent}{0in}
\setlength{\parskip}{0in}
\setlength{\itemsep}{0in}
\setlength{\topsep}{0in}
\setlength{\tabcolsep}{0in}

% Name and contact information
\newcommand{\name}{Bryan Tidwell}
\newcommand{\email}{\href{mailto:bryanktidwell2@gmail.com}{bryanktidwell2@gmail.com}}
\newcommand{\phone}{615 310-5829}
\newcommand{\github}{\url{https://github.com/DwordPtr}}
\newcommand{\linkedin}{\url{https://www.linkedin.com/in/bryantidwell2}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% New commands and environments

% This defines how the name looks
\newcommand{\bigname}[1]{
	\begin{center}\fontfamily{phv}\selectfont\LARGE\scshape#1\end{center}
}

% A ressection is a main section (<H1>Section</H1>)
\newenvironment{ressection}[1]{
	\vspace{4pt}
	{\fontfamily{phv}\selectfont\Large#1}
	\begin{itemize}
	\vspace{3pt}
}{
	\end{itemize}
}

% A resitem is a simple list element in a ressection (first level)
\newcommand{\resitem}[1]{
	\vspace{-4pt}
	\item \begin{flushleft} #1 \end{flushleft}
}

% A ressubitem is a simple list element in anything but a ressection (second level)
\newcommand{\ressubitem}[1]{
	\vspace{-1pt}
	\item \begin{flushleft} #1 \end{flushleft}
}

% A resbigitem is a complex list element for stuff like jobs and education:
%  Arg 1: Name of company or university
%  Arg 2: Location
%  Arg 3: Title and/or date range
\newcommand{\resbigitem}[3]{
	\vspace{-5pt}
	\item
	\textbf{#1}---#2 \\
	\textit{#3}
}

% This is a list that comes with a resbigitem
\newenvironment{ressubsec}[3]{
	\resbigitem{#1}{#2}{#3}
	\vspace{-2pt}
	\begin{itemize}
}{
	\end{itemize}
}

% This is a simple sublist
\newenvironment{reslist}[1]{
	\resitem{\textbf{#1}}
	\vspace{-5pt}
	\begin{itemize}
}{
	\end{itemize}
}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Now for the actual document:

\begin{document}

\fontfamily{ptm} \selectfont

% Name with horizontal rule
\bigname{\name}

\begin{center} Java 8 \textperiodcentered \ Maven \textperiodcentered \ Gradle \textperiodcentered 
        \ SpringBoot \textperiodcentered \ Spring \textperiodcentered \ Struts \textperiodcentered \ JSP \textperiodcentered \ Bash \textperiodcentered \ SQL  \textperiodcentered \ Hibernate \textperiodcentered \ Junit \textperiodcentered \ Intellij
\end{center}
\vspace{-1pt} {\small \linkedin \small \hfill \email} \\
\vspace{-1pt} {\small \github \small \hfill \ifdefined\unredacted \phone \fi} \\

%%%%%%%%%%%%%%%%%%%%%%%%
\begin{ressection}{Experience}
        \begin{ressubsec}{Atiba}{Nashivlle, TN}{Software Engineer Nov 2017 - Aug 2019}
		\ressubitem{Implemented core idioms in Java for full Android application UI redesign.}
		\ressubitem{Setup Jenkins for an Android application.}
        \ressubitem{Primary author of Elixir service for Nest thermostat integrations with Dynamodb and \href{https://github.com/ex-aws/ex\_aws}{ExAws}.}
        \ressubitem{Contributed support for https streaming options in \href{https://github.com/cwc/eventsource_ex/pull/10/files}{eventsource\_ex (old work account).}}
        \ressubitem{Implemented hardware simulator using socat and pymodbus for testing an industrial IoT application.}
        \ressubitem{Re-implemented endpoint in C daemon from json to base64 significantly increasing graphing speed for Android application.}
		\ressubitem{Fixed client init script to prevent test Java appliance from contacting production.}
        \ressubitem{Worked with Cucumber for client BDD transition.}
	\end{ressubsec}

			\begin{ressubsec}{Franklin American Mortgage Company}{Franklin, TN}{Developer I Mar 2016 - Nov 2017}
                    \ressubitem{Contributed to Java test framework called \href{https://github.com/mockrunner/mockrunner/pull/42}{MockRunner}.}
		\ressubitem{Maintained business critical legacy Java 6 apps.}
        \ressubitem{Worked on Spring Boot microservice (Java 8) to integrate customer data with Salesforce.}
        \ressubitem{Added new trigger extension to highlighting scheme for salesforce \href{https://github.com/ejholmes/vim-forcedotcom/pull/13}{vim plugin}.}
	\end{ressubsec}

	\begin{ressubsec}{Comdata}{Brentwood, TN}{Business Objects Analyst (Intern then 1099 contractor) May 2014 - Dec 2014}
    \ressubitem{Used scripting tools to extend automated tests.}
    \ressubitem{Retained as contractor on a mostly remote basis, after the internship.}
	\end{ressubsec}

\end{ressection}

%%%%%%%%%%%%%%%%%%%%%%%%
\begin{ressection}{Education}

	\begin{ressubsec}{Austin Peay State University}{Clarksville, TN}{Major in Computer Science with Minors in Mathematics and Philosophy Dec, 2015}
		\ressubitem{GPA: 3.65 \textit{Cum Laude} ( $\approx 3.8$ Computer Science GPA)}
		\ressubitem{Awarded George Brotherton memorial scholarship.}
	\end{ressubsec}
\end{ressection}

\begin{ressection}{Skills}
	\begin{reslist}{Programming Languages \& Tooling:}
        \ressubitem{Extensive experience in Java (3.5 years).}
        \ressubitem{Used both xml based Spring config and annotation based with SpringBoot.}
        \ressubitem{Experience with Hibernate in large enterprise system.}
		\ressubitem{Comfortable with Modern OOP and functional programming.}
		\ressubitem{Capable with shell scripting and various devops tools.}
		\ressubitem{Knowledgeable interfacing with databases in SQL and through ORMs.}
        \ressubitem{Worked with at least one NoSql database (Dynamodb)}
		\ressubitem{Skilled in dynamically and statically typed languages. }
		\ressubitem{Experience automating repetitive tasks with python, bash and zsh.}
		\ressubitem{Employed various cloud services like Ayla and Dynamodb.}
\end{reslist}
\end{ressection}
\end{document}
